Compositional Certified Resource Bounds\ifshort{\vspace{-1.15cm}}{}

### 2014-11-11 paper/main.tex
still working on section 3

\begin{figure*}
 \setlength{\progwidth}{.30\linewidth}
  \centering
\hspace{-0.4cm}
  \begin{minipage}[b]{.4\linewidth}
    \begin{center}
   \begin{lstlisting}[]
void count_down (int x,int y) {
  if (x>y) { tick(1); count_up(x-1,y);}
}
void count_up (int x, int y) {
  if (y+1<x) { tick(1); count_down(x,y+2);}
}
   \end{lstlisting}
\vspace{-2.5ex}
$0.33 + 0.67 |[y,x]|\;\;$ (\code{count\_down(x,y)})\\
$\;\;\;\;\;\;\,0.67 |[y,x]|\;\;$ (\code{count\_up(x,y)})
\\[.4\baselineskip]
      {\bf t39}
    \end{center}
  \end{minipage}
%
\hfill
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}

   \end{lstlisting}
\vspace{-2.5ex}
$XXX$
\\[.4\baselineskip]
      {\bf XXX}
    \end{center}
  \end{minipage}
%
\hfill
%
  \begin{minipage}[b]{\progwidth}
    \begin{center}
   \begin{lstlisting}

   \end{lstlisting}
\vspace{-2.5ex}
$XXX$
\\[.4\baselineskip]
      {\bf XXX}
    \end{center}
  \end{minipage}
\vspace{1ex}
\caption{Exampel \emph{t39} shows two mutually-recursive functions
  with the computed tick bounds.  The derived constant factors are
  tight.}
  \label{fig:ex_list_2}
\end{figure*}

@@

As mentioned, the analysis also handles advanced control flow like
\code{break} and \code{return} statements, and mutual recursion.
Example \emph{t39} in \pref{fig:ex_list_2} contains two mutually-recursive functions with their
automatically derived tick bounds.  The function \code{count\_down}
decrements its first argument $x$ until it reaches the second argument
$y$. It then recursively calls the function \code{count\_up},
which is dual to \code{count\_down}.  Here, we
count up $y$ by $2$ and recursively call \code{count\_down}.  $\toolname$ is 
the only available system that computes a tight
bound.  \iffull{The analysis amounts to computing the meeting
point of two trains that approach each other with different speeds.}{}
% This is comparable to the
% determination of the point at which to trains meet if they approach
% each other with different speeds.

>>>>

\begin{figure*}
  \centering
\hspace{-0.4cm}
  \begin{minipage}[b]{7cm}
    \begin{center}
   \begin{lstlisting}[]
void c_down (int x,int y) {
  if (x>y) { tick(1); c_up(x-1,y); }
}
void c_up (int x, int y) {
  if (y+1<x) {tick(1); c_down(x,y+2);}
}
   \end{lstlisting}
\vspace{-2.5ex}
$0.33 + 0.67 |[y,x]|\;\;$ (\code{c\_down(x,y)})\\
$\;\;\;\;\;\;\,0.67 |[y,x]|\;\;$ (\code{c\_up(x,y)})
\\[.4\baselineskip]
      {\bf t39}
    \end{center}
  \end{minipage}
%
\hfill
%
  \begin{minipage}[b]{5cm}
    \begin{center}
   \begin{lstlisting}
for (; l >= 8; l -= 8)
  // process one block
  tick(N);
for (; l > 0; l--)
  // save leftovers
  tick(1);
   \end{lstlisting}
\vspace{-2.5ex}
$XXX$
\\[.4\baselineskip]
      {\bf t61}
    \end{center}
  \end{minipage}
%
\hfill
%
  \begin{minipage}[b]{5.5cm}
    \begin{center}
   \begin{lstlisting}

   \end{lstlisting}
\vspace{-2.5ex}
\begin{lstlisting}
for (;;) {
  do { l++; tick(1); } 
    while (l < h && *);
  do { h--; tick(1); } 
    while (h > l && *);
  if (h <= l) break;
  tick(1); /* swap elems. */ }
\end{lstlisting}
$XXX$
\\[.4\baselineskip]
      {\bf t62}
    \end{center}
  \end{minipage}
\vspace{1ex}
\caption{Exampel \emph{t39} shows two mutually-recursive functions
  with the computed tick bounds.  The derived constant factors are
  tight.}
  \label{fig:ex_list_2}
\end{figure*}

@@

As mentioned, the analysis also handles advanced control flow like
\code{break} and \code{return} statements, and mutual recursion.
Example \emph{t39} in \pref{fig:ex_list_2} contains two mutually-recursive functions with their
automatically derived tick bounds.  The function \code{c\_down}
decrements its first argument $x$ until it reaches the second argument
$y$. It then recursively calls the function \code{c\_up},
which is dual to \code{c\_down}.  Here, we
c up $y$ by $2$ and recursively call \code{c\_down}.  $\toolname$ is 
the only available system that computes a tight
bound.  \iffull{The analysis amounts to computing the meeting
point of two trains that approach each other with different speeds.}{}
% This is comparable to the
% determination of the point at which to trains meet if they approach
% each other with different speeds.
